systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-06-21 paper/trunk/JSS/response_A.tex

\begin{document}
\begin{center}
{\Large\textbf{
systemfit: A Package to Estimate
Simultaneous Equation Systems in R (JSS~224)}}

\bigskip

{\Large\textbf{Responses to Reviewer A}}
\end{center}

We thank this reviewer for her/his very helpful comments and suggestions
that assisted us to considerably improve the software as well as the paper.
The reviewer has made one overall comment, 9 major comments and
several minor comments.
We have structured our reply accordingly.

\section{Overall Comment}
% ########################################################
% ## Review for                                         ##
% ##   systemfit: A Package to Estimate Simultaneous    ##
% ##   Equation Systems in R                            ##
% ##   Arne Henningsen, Jeff D. Hamann                  ##
% ## submitted for publication in                       ##
% ##   Journal of Statistical Software                  ##
% ########################################################
% 
% The paper describes the CRAN package "systemfit" for fitting simultaneous
% equation models in R. Estimation procedures include standard techniques in
% econometrics such as SUR, 2SLS and 3SLS.
% The paper can be divided roughly into three parts: Sections 1/2 explain
% the underlying theory (~12 pages), Sections 3/4 describe the code in systemfit
% and how to use it (~10 pages) and Section 5 reproduces results from various
% textbooks (~8 pages).
% The paper and software are both interesting and mostly well-written: they
% deserve publication in JSS. However, some major and minor comments have to
% be addressed before it can be accepted. In particular, the revision has to
% streamline exposition and notation of standard results, and to combine the
% (established) theory with the implementation more closely (otherwise the reader
% has to wait more than 10 pages before s/he learns something about the package).
% I suggest to eliminate Section 2 in its current form and to re-write the
% description of the theory in a more general and unified way while weaving
% it with the translation into computational tools.
We consider the presentation of the theoretical background
in a separate section
as an advantage rather than as a drawback.
As the formulas to calculate the estimators and their covariances
are not essential to \emph{use} \pkg{systemfit},
we think that the formulas and the usage should not be presented together.
Furthermore, our structure allows readers
who already know the theoretical background
to skip this entire section
and go immediately into the section they are interested in
(e.g.\ section °Using systemfit°).
Hence, they do not have to scan a large composite section
just to figure out a few commands of \pkg{systemfit}.
Readers who have skipped the section °Statistical background°,
can easily go back to this section
if they are interested in a particular part of the theory,
because all parts in section °Using systemfit°
have references to their theoretical background
in section °Statistical background°.

% As for the software itself,
% several modifications are necessary to make it more intuitive for R users
% and to improve how the underlying concepts are turned into computational 
% tools. More details are described below.
% 
% 
\section{Major Points}
% MAJOR POINTS:
\subsection{Title}
%   o title
% 
%     The title sounds a bit awkward in English: first, "a package *for*
%     estimat*ing*" would be more appropriate, secondly "systems of
%     equations" seems to be preferred over "equation systems" in English.
%
We have changed the title according to these suggestions.

### 2007-06-22 paper/trunk/JSS/response_A.tex

\begin{document}
\begin{center}
{\Large\textbf{
systemfit: A Package to Estimate
Simultaneous Equation Systems in R (JSS~224)}}

\bigskip

{\Large\textbf{Responses to Reviewer A}}
\end{center}

We thank this reviewer for her/his very helpful comments and suggestions
that assisted us to considerably improve the software as well as the paper.
The reviewer has made one overall comment, 9 major comments and
several minor comments.
We have structured our reply accordingly.

\section{Overall Comment}
% ########################################################
% ## Review for                                         ##
% ##   systemfit: A Package to Estimate Simultaneous    ##
% ##   Equation Systems in R                            ##
% ##   Arne Henningsen, Jeff D. Hamann                  ##
% ## submitted for publication in                       ##
% ##   Journal of Statistical Software                  ##
% ########################################################
% 
% The paper describes the CRAN package "systemfit" for fitting simultaneous
% equation models in R. Estimation procedures include standard techniques in
% econometrics such as SUR, 2SLS and 3SLS.
% The paper can be divided roughly into three parts: Sections 1/2 explain
% the underlying theory (~12 pages), Sections 3/4 describe the code in systemfit
% and how to use it (~10 pages) and Section 5 reproduces results from various
% textbooks (~8 pages).
% The paper and software are both interesting and mostly well-written: they
% deserve publication in JSS. However, some major and minor comments have to
% be addressed before it can be accepted. In particular, the revision has to
% streamline exposition and notation of standard results, and to combine the
% (established) theory with the implementation more closely (otherwise the reader
% has to wait more than 10 pages before s/he learns something about the package).
% I suggest to eliminate Section 2 in its current form and to re-write the
% description of the theory in a more general and unified way while weaving
% it with the translation into computational tools.
We appreciate this recommendation of the reviewer very much,
but we consider the presentation of the theoretical background
in a separate section
as an advantage rather than as a drawback.
As the formulas to calculate the estimators and their covariances
are not essential to \emph{use} \pkg{systemfit},
we think that the formulas and the usage should be presented separately.
Furthermore, our structure allows readers
who already know the theoretical background
(or who do not want to know it)
to skip this entire section
and to go immediately into the section they are interested in
(e.g.\ section °Using systemfit°).
Hence, they do not have to scan a large composite section
just to figure out a few pieces of information
(e.g.\ how to use the commands of \pkg{systemfit}).
Readers who have skipped the °Statistical background°
can easily go back to this section
if they are interested in a particular part of the theory,
because all parts in section °Using systemfit°
have references to their theoretical background
in section °Statistical background°.

% As for the software itself,
% several modifications are necessary to make it more intuitive for R users
% and to improve how the underlying concepts are turned into computational 
% tools. More details are described below.
% 
% 
\section{Major Points}
% MAJOR POINTS:
\subsection{Title}
%   o title
% 
%     The title sounds a bit awkward in English: first, "a package *for*
%     estimat*ing*" would be more appropriate, secondly "systems of
%     equations" seems to be preferred over "equation systems" in English.
%
We have changed the title according to these suggestions.

### 2007-06-22 paper/trunk/JSS/response_A.tex

% As for the software itself,
% several modifications are necessary to make it more intuitive for R users
% and to improve how the underlying concepts are turned into computational 
% tools. More details are described below.
As suggested by this reviewer,
the software package \pkg{systemfit} has been considerably modified
to make it more intuitive for \proglang{R} users.
We tried to make the usage of \pkg{systemfit}
as close as possible to the primary regression tools in \proglang{R}
(e.g.\ \code{lm}).
More details of theses modifications are described below.

% 
% 
\section{Major Points}
% MAJOR POINTS:
\subsection{Title}
%   o title
% 
%     The title sounds a bit awkward in English: first, "a package *for*
%     estimat*ing*" would be more appropriate, secondly "systems of
%     equations" seems to be preferred over "equation systems" in English.
%
We have changed the title according to these suggestions.

### 2007-06-22 paper/trunk/JSS/response_A.tex

\documentclass[12pt,english]{scrartcl}
\input{response_commands}

\begin{document}
\begin{center}
{\Large\textbf{\textsf{
systemfit: A Package for Estimating\\[0.3em]
Systems of Simultaneous Equations in \proglang{R} (JSS~224)%
\footnote{
The original title was: °systemfit: A Package to Estimate
Simultaneous Equation Systems in \proglang{R}°.}
}}}

### 2007-06-22 paper/trunk/JSS/response_A.tex

% As for the software itself,
% several modifications are necessary to make it more intuitive for R users
% and to improve how the underlying concepts are turned into computational 
% tools. More details are described below.
As suggested by this reviewer,
the software package \pkg{systemfit} has been considerably modified
to make it more intuitive for \proglang{R} users.
We tried to make the usage of \pkg{systemfit}
as close as possible to the primary regression tools in \proglang{R}
(e.g.\ \code{lm}).
More details of theses modifications are described below.

% 
% 
\section{Major Points}
% MAJOR POINTS:
\subsection{Title}
%   o title
% 
%     The title sounds a bit awkward in English: first, "a package *for*
%     estimat*ing*" would be more appropriate, secondly "systems of
%     equations" seems to be preferred over "equation systems" in English.
%
We have changed the title according to these suggestions.

\subsection{Abstract/Introduction}
%   o abstract/introduction
% 
%     Both, abstract and introduction, talk rather generally about
%     systems of equations reviewing rather well-known theoretical
%     results. I would suggest to revise both, focusing on what
%     *can* be done *in R* rather than giving a tutorial what *should*
%     be done *in general*. Of course, it is ok to review some theory,
%     however, practitioners should know what they are doing and the
%     paper should mainly teach them how to do it in R.
%
Both, abstract and introduction, now focus much more
on the capabilities of the \pkg{systemfit} package
rather than on the general theory of estimating systems of equations.

\subsection{Estimation Methods (2.1)}
%   o estimation methods (2.1)
% 
%     The description of the estimation methods can be shortened considerably
%     and should focus on the unifying properties of the different estimators.
%     All methods from OLS through to standard 3SLS comply with formulas
%     (12) and (13), only with differing choices for Omega (s*I, diagonal or
%     full Omega) and X (original X vs \hat X from instruments). The exposition
%     could be streamlined considerably if this structure were exploited.
% 
The reviewer is right that it is possible to shorten
the description of the estimation methods
by exploiting the common properties of the different estimators.
However, in our opinion this shortening would considerably worsen
the readability of this section.
Furthermore, a major purpose of this section is
that a user of the \pkg{systemfit} package
can take a look at the theory (e.g.\ formulas) of a specific estimation method.
Therefore, we fully describe each estimation method
in a single (subsub)section.

@@

In our opinion,
it is not desirable to relax the requirement
of using the same formula for all equations
in (classical) °Seemingly Unrelated Regression° analyses
with panel-like data.
First, it would be rather cumbersome for the user to specify,
which formula should be applied to which (cross-section) individual.
Second, this type of analysis can be easily done
by reshaping the data (e.g.\ with \code{reshape})
and then using (standard) \code{systemfit}.
Third, we think that this feature would rarely be used.

%     Second, the interface should also be re-designed: the standard in R is
%     that the formula/s is/are the first argument (which would also be more
%     convenient for systemfit()), e.g.,
%       function(formula, method = "FGLS", data = ..., ...)
%     Currently, the data argument seems to be mandatory (opposed to the
%     paper documentation). The specification of eqnVar and timeVar via
%     strings seems to be uncommon and suboptimal. Probably some kind of
%     formula would be preferable. Maybe a formula similar to those used in
%     nlme could be employed? If more than one formula is specified, one has
%     to pay attention that no problems are used by different patterns of
%     missingness in differing equations.
%
All remaining concerns regarding \code{systemfitClassic}
(order of arguments;
argument \code{data} being mandatory;
arguments \code{eqnVar} and \code{timeVar} being strings)
have been resolved by its removal.

\subsection{Testing Linear Restrictions (4.4)}
%   o testing linear restrictions (4.4)
% 
%     The package introduces several functions that are somewhat orthogonal
%     to exisiting methodology. A single method (with "test" argument) for
%     the linear.hypothesis() function from "car" might seem more appropriate
%     here. The Wald test can already now be reproduced using the default
%     linear.hypothesis() method (except for formula formatting)
%       linear.hypothesis(fitsur, Rmat, qvec)    
%     If the coefficient naming would be modified (see below), the convenience
%     interface for specifying the restrictions in linear.hypothesis() could
%     also be re-used.    
%     Also two of the functions look like methods to the generics lrtest() and
%     waldtest() in package "lmtest", although this is not the case. Furthermore,
%     some more general method of comparing various fitted models would be nice,
%     e.g., an anova() method or methods to waldtest()/lrtest() although the 
%     latter two seem to be under development.
%     The output formatting of the current function is also not very elegant,
%     a new class along with its print method is introduced for each test. It
%     would be much easier to re-use "htest" or (probably better) "anova" as
%     classes for this.
We have modified the tools for testing linear hypothesis
according to the suggestions of this reviewer.
The user can test linear restrictions by a Wald/$\chi^2$ or F test
using the generic function \code{linear.hypothesis} now.
The method \code{linear.hypothesis.systemfit} uses
\code{linear.}\hspace{0pt}\code{hypothesis.}\hspace{0pt}\code{default}
of the \pkg{car} package
to compute the Wald/$\chi^2$ statistic.
The $F$ statistic is computed in the \pkg{systemfit} package internally,
but the returned object is of the same class and structure
as the result of \code{linear.hypothesis.default}.

The method \code{lrtest.systemfit} is a wrapper function
to \code{lrtest.default} of the \pkg{lmtest} package now.
Its main task is to specify the names for the compared objects.

%
\subsection{Organize Internals of systemfit}
%   o organize internals of systemfit
% 
%     The internals of a fitted "systemfit" object could be re-organized. Currently,
%     there are a lot of single letter elements - more standard naming as in "lm"
%     objects etc. would be more desirable.
We have renamed single letter elements (not finished yet).

### 2007-06-27 paper/trunk/JSS/response_A.tex

The method \code{lrtest.systemfit} is a wrapper function
to \code{lrtest.default} of the \pkg{lmtest} package now.
Its main task is to specify the names for the compared objects.

%
\subsection{Organize Internals of systemfit}
%   o organize internals of systemfit
% 
%     The internals of a fitted "systemfit" object could be re-organized. Currently,
%     there are a lot of single letter elements - more standard naming as in "lm"
%     objects etc. would be more desirable.
We have renamed single letter elements (not finished yet).

%     Also, computing the partial t tests
%     should/could be done in the summary() method, avoiding that certain parameters
%     (not affecting the fit itself, such as degrees of freedom) necessarily have to
%     be specified for model fitting.
% 
%     The technical control parameters could also be collected in a list of arguments, e.g.,
%       control = systemfit.control()
%     that sets suitable defaults but can also easily be changed. If possible `...'
%     arguments could be passed to systemfit.control() assuring backward compatibility
%     and facilitating interactive usage.
Following the suggestion of this referee,
the technical control parameters of \code{systemfit()} are collected
in a single argument \code{control} now.
This argument is a list that contains the technical control parameters,
where suitable default values are set by the function
\code{systemfit.control()}.

%     The names of various
%     arguments should be re-thought, e.g. "tx", "R.restr" and "q.rests" seem rather
%     arbitrary. Similar comments hold for other arguments, see also below for some
%     more comments.
The names of several arguments have been improved.
The arguments to impose parameter restrictions by $R \beta = q$
(former \code{R.restr} and \code{q.restr})
have been renamed to \code{restrict.matrix} and \code{restrict.rhs},
respectively
(following the arguments \code{hypothesis.matrix} and \code{rhs}
of the generic function \code{linear.hypothesis}).
The argument to impose parameter restrictions
by modifying (post-multiplying) the regressor matrix
(fromer \code{TX}) has been renamed to \code{restrict.regMat}.
Finally, the arguments to specify the methods
for the 3SLS estimation and to calculated the residual covariance matrix
(former \code{formula3sls} and \code{rcovformula})
have been renamed to \code{method3sls} and \code{methodRCov},
respectively.

%     As noted above, the standard in R seems to supply the formula(s)
%     as the first argument and to have then some `method' argument.
We have reversed the order of arguments \code{method} and \code{eqns}
of \code{systemfit()}.
It is no longer necessary to reverse the order of the arguments
of \code{systemfitClassic()},
because this function has been removed.

### 2007-06-27 paper/trunk/JSS/response_A.tex

The method \code{lrtest.systemfit} is a wrapper function
to \code{lrtest.default} of the \pkg{lmtest} package now.
Its main task is to specify the names for the compared objects.

%
\subsection{Organize Internals of systemfit}
%   o organize internals of systemfit
% 
%     The internals of a fitted "systemfit" object could be re-organized. Currently,
%     there are a lot of single letter elements - more standard naming as in "lm"
%     objects etc. would be more desirable.
We have renamed single letter elements (not finished yet).

%     Also, computing the partial t tests
%     should/could be done in the summary() method, avoiding that certain parameters
%     (not affecting the fit itself, such as degrees of freedom) necessarily have to
%     be specified for model fitting.
Furthermore, we have followed the advice of this referee
and moved the computation of the partial $t$ statistic
from the \code{systemfit()} function to its \code{summary()} method.

% 
%     The technical control parameters could also be collected in a list of arguments, e.g.,
%       control = systemfit.control()
%     that sets suitable defaults but can also easily be changed. If possible `...'
%     arguments could be passed to systemfit.control() assuring backward compatibility
%     and facilitating interactive usage.
Following the suggestion of this referee,
the technical control parameters of \code{systemfit()} are collected
in a single argument \code{control} now.
This argument is a list that contains the technical control parameters,
where suitable default values are set by the function
\code{systemfit.control()}.

@@

%     The names of various
%     arguments should be re-thought, e.g. "tx", "R.restr" and "q.rests" seem rather
%     arbitrary. Similar comments hold for other arguments, see also below for some
%     more comments.
The names of several arguments have been improved.
The arguments to impose parameter restrictions by $R \beta = q$
(former \code{R.restr} and \code{q.restr})
have been renamed to \code{restrict.matrix} and \code{restrict.rhs},
respectively
(following the arguments \code{hypothesis.matrix} and \code{rhs}
of the generic function \code{linear.hypothesis}).
The argument to impose parameter restrictions
by modifying (post-multiplying) the regressor matrix
(fromer \code{TX}) has been renamed to \code{restrict.regMat}.
Finally, the arguments to specify the methods
for the 3SLS estimation and to calculated the residual covariance matrix
(former \code{formula3sls} and \code{rcovformula})
have been renamed to \code{method3sls} and \code{methodRCov},
respectively.

%     As noted above, the standard in R seems to supply the formula(s)
%     as the first argument and to have then some `method' argument.
We have reversed the order of arguments \code{method} and \code{eqns}
of \code{systemfit()}.
It is no longer necessary to reverse the order of the arguments
of \code{systemfitClassic()},
because this function has been removed.

% 
%     Some more standard elements of a model fit should also be kept, in particular
%     the call so that update() can work with "systemfit" objects, e.g.,
%       fitsur <- systemfit("SUR", list(demand = eqDemand, supply = eqSupply))
%       fitsur$call <- call("systemfit", "SUR", list(demand = eqDemand, supply = eqSupply))
%       fitsurRmat <- update(fm, R.restr = Rmat, q.restr = qvec)
%     The call can easily be captured via match.call().
The call of \code{systemfit} is stored in the returned object now.
This allows the application of \code{update()} to \code{systemfit} objects.

%     Similarly, one could think 
%     about how the terms and formula can be preserved and possibly made available
%     in terms() and formula() calls. Other standard methods would also be nice to have,
%     e.g., df.residual() or logLik(). (By the way: The row/column naming in fitted()
%     and residuals() should match, probably re-using equation and observation names.)
% 
%     The coefficient naming should be improved, e.g., "<eqname>_<varname>"
%     where <eqname> can be set by default to "eq1", "eq2" etc. but should use the
%     equation names (if supplied). Spaces in names should be avoided.
%     The coefficient naming in the systemfitClassic() interface could also be 
%     improved, see e.g. the output on p.27, l.546: "eq 2 capital.Chrysler" redundantly
%     codes the firm (both by eq and name) and "Chrysler_capital" or "Chryler.capital"
%     would be preferable.
The naming of the coefficients has been improved
according to the suggestions of this referee:
they are now \code{<eqname>}\verb!_!\code{<varname>},
where \code{<eqname>} is the equation name,
which is set to \code{"eq1"}, \code{"eq2"} etc.\
if no equation names are supplied by the user.
In the case of a (classical) °Seemingly Unrelated Regression° analysis
with panel-like data,
all redundant parts of the coefficient names have been removed:
the coefficient names in the vector of all coefficients are
\code{<individual>}\verb!_!\code{<varname>}
and the coefficient names in the vector of the coefficients of a single
individual are just \code{<varname>}.

### 2007-06-27 paper/trunk/JSS/response_A.tex

%     The names of various
%     arguments should be re-thought, e.g. "tx", "R.restr" and "q.rests" seem rather
%     arbitrary. Similar comments hold for other arguments, see also below for some
%     more comments.
The names of several arguments have been improved.
The arguments to impose parameter restrictions by $R \beta = q$
(former \code{R.restr} and \code{q.restr})
have been renamed to \code{restrict.matrix} and \code{restrict.rhs},
respectively
(following the arguments \code{hypothesis.matrix} and \code{rhs}
of the generic function \code{linear.hypothesis}).
The argument to impose parameter restrictions
by modifying (post-multiplying) the regressor matrix
(fromer \code{TX}) has been renamed to \code{restrict.regMat}.
Finally, the arguments to specify the methods
for the 3SLS estimation and to calculated the residual covariance matrix
(former \code{formula3sls} and \code{rcovformula})
have been renamed to \code{method3sls} and \code{methodRCov},
respectively.

%     As noted above, the standard in R seems to supply the formula(s)
%     as the first argument and to have then some `method' argument.
We have reversed the order of arguments \code{method} and \code{eqns}
of \code{systemfit()}.
It is no longer necessary to reverse the order of the arguments
of \code{systemfitClassic()},
because this function has been removed.

% 
%     Some more standard elements of a model fit should also be kept, in particular
%     the call so that update() can work with "systemfit" objects, e.g.,
%       fitsur <- systemfit("SUR", list(demand = eqDemand, supply = eqSupply))
%       fitsur$call <- call("systemfit", "SUR", list(demand = eqDemand, supply = eqSupply))
%       fitsurRmat <- update(fm, R.restr = Rmat, q.restr = qvec)
%     The call can easily be captured via match.call().
The call of \code{systemfit} is stored in the returned object now.
This allows the application of \code{update()} to \code{systemfit} objects.

%     Similarly, one could think 
%     about how the terms and formula can be preserved and possibly made available
%     in terms() and formula() calls. Other standard methods would also be nice to have,
%     e.g., df.residual() or logLik().
Following the suggestions of this referee,
the °model terms° (including the formulas) of each equation are preserved now.
We have added methods \code{terms.systemfit}, \code{terms.systemfit.equation},
\code{formula.systemfit}, and \code{formula.systemfit.equation}
to extract the °model terms° and formulas
of the system and of a single equation.
The new method \code{logLik} computes the log-likelihood value
of a fitted \code{systemfit} object.
Furthermore, the default method of \code{df.residual}
can extract the degrees of freedom of the residuals,
both of the system and of a single equation now.

%     (By the way: The row/column naming in fitted()
%     and residuals() should match, probably re-using equation and observation names.)
% 
%     The coefficient naming should be improved, e.g., "<eqname>_<varname>"
%     where <eqname> can be set by default to "eq1", "eq2" etc. but should use the
%     equation names (if supplied). Spaces in names should be avoided.
%     The coefficient naming in the systemfitClassic() interface could also be 
%     improved, see e.g. the output on p.27, l.546: "eq 2 capital.Chrysler" redundantly
%     codes the firm (both by eq and name) and "Chrysler_capital" or "Chryler.capital"
%     would be preferable.
The naming of the coefficients has been improved
according to the suggestions of this referee:
they are now \code{<eqname>}\verb!_!\code{<varname>},
where \code{<eqname>} is the equation name,
which is set to \code{"eq1"}, \code{"eq2"} etc.\
if no equation names are supplied by the user.
In the case of a (classical) °Seemingly Unrelated Regression° analysis
with panel-like data,
all redundant parts of the coefficient names have been removed:
the coefficient names in the vector of all coefficients are
\code{<individual>}\verb!_!\code{<varname>}
and the coefficient names in the vector of the coefficients of a single
individual are just \code{<varname>}.

### 2007-06-27 paper/trunk/JSS/response_A.tex

%
\subsection{Organize Internals of systemfit}
%   o organize internals of systemfit
% 
%     The internals of a fitted "systemfit" object could be re-organized. Currently,
%     there are a lot of single letter elements - more standard naming as in "lm"
%     objects etc. would be more desirable.
We have renamed single letter elements (not finished yet).

%     Also, computing the partial t tests
%     should/could be done in the summary() method, avoiding that certain parameters
%     (not affecting the fit itself, such as degrees of freedom) necessarily have to
%     be specified for model fitting.
Furthermore, we have followed the advice of this referee
and moved the computation of the partial $t$ statistic
from the \code{systemfit()} function to its \code{summary()} method.

% 
%     The technical control parameters could also be collected in a list of arguments, e.g.,
%       control = systemfit.control()
%     that sets suitable defaults but can also easily be changed. If possible `...'
%     arguments could be passed to systemfit.control() assuring backward compatibility
%     and facilitating interactive usage.
Following the suggestion of this referee,
the technical control parameters of \code{systemfit()} are collected
in a single argument \code{control} now.
This argument is a list that contains the technical control parameters,
where suitable default values are set by the function
\code{systemfit.control()}.

%     The names of various
%     arguments should be re-thought, e.g. "tx", "R.restr" and "q.rests" seem rather
%     arbitrary. Similar comments hold for other arguments, see also below for some
%     more comments.
The names of several arguments have been improved.
The arguments to impose parameter restrictions by $R \beta = q$
(former \code{R.restr} and \code{q.restr})
have been renamed to \code{restrict.matrix} and \code{restrict.rhs},
respectively
(following the arguments \code{hypothesis.matrix} and \code{rhs}
of the generic function \code{linear.hypothesis}).
The argument to impose parameter restrictions
by modifying (post-multiplying) the regressor matrix
(former \code{TX}) has been renamed to \code{restrict.regMat}.
Finally, the arguments to specify the methods
for the 3SLS estimation and to calculated the residual covariance matrix
(former \code{formula3sls} and \code{rcovformula})
have been renamed to \code{method3sls} and \code{methodRCov},
respectively.

### 2007-06-28 paper/trunk/systemfit_compare_lm.tex
aligned latex code of table that compares the objects returned by lm and systemfit
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@762 591db2bd-e0a0-4d22-8c19-2192dbb7da31
table that compares the objects returned by lm and systemfit: updated elements of systemfit objects due to changes of the systemfit package
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@763 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\begin{table}[htbp]
\caption{Values returned by systemfit and lm}
\begin{tabular}{lll}
\hline
lm & systemfit & systemfit.equation \\
\hline
coefficients & coefficients & coefficients \\
residuals & & residuals \\
fitted.values & & fitted.values \\
rank & rank & rank \\
 & & rank.sys \\
 & & nCoef.sys \\
weights & & \\
df.residual & df.residual & df.residual \\
 & & df.residual.sys \\
call & call & \\
terms & & terms \\
contrasts & & \\
xlevels & & \\
offset & & \\
y** & & response* \\
x** & & modelMatrix* \\
 & & instMatrix* \\
model* & & modelFrame* \\
 & method & \\
 & & eqnLabel \\
 & iter & \\
 & bt & \\
 & bcov & covb \\
 & btcov & \\
 & rcov & \\
 & rcovest & \\
 & R.restr & \\
 & q.restr & \\
 & TX & \\
 & control & \\
 & eq & \\
 & & inst \\
 & & ssr \\
 & & sigma \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Values returned by systemfit and lm}
\begin{tabular}{lll}
\hline
lm & systemfit & systemfit.equation \\
\hline
coefficients    & coefficients   & coefficients \\
residuals       &                & residuals \\
fitted.values   &                & fitted.values \\
rank            & rank           & rank \\
                &                & rank.sys \\
                &                & nCoef.sys \\
weights         &                & \\
df.residual     & df.residual    & df.residual \\
                &                & df.residual.sys \\
call            & call           & \\
terms           &                & terms \\
contrasts       &                & \\
xlevels         &                & \\
offset          &                & \\
y**             &                & response* \\
x**             &                & modelMatrix* \\
                &                & instMatrix* \\
model*          &                & modelFrame* \\
                & method         & method \\
                &                & eqnLabel \\
                &                & eqnNo \\
                & iter           & \\
                & coefCov        & coefCov \\
                & residCov       & \\
                & residCovEst    & \\
                & restrict.matrix& \\
                & restrict.rhs   & \\
                & restrict.regMat& \\
                & control        & \\
                & eq             & \\
                & panelLike      & \\
                &                & inst \\
                &                & ssr \\
                &                & sigma \\
\hline
\end{tabular}
\end{table}
